---
title: "Introduction"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message=FALSE}
library(tidyverse)
library(actsims)
```

## Set up

First, create an "`InteRactModel`" R6 object.

```{r example}
act <- interact(dictionary = "usfullsurveyor2015", equations = "us2010")
act
```

_Dictionary_

```{r}
act$dictionary
```

_Equations_

```{r}
act$equations
```

`interact()` uses `group = all` by default for both equations and dictionaries. If this option does not exist in the `actdata` package, then you will see an error.

```{r, error=TRUE}
interact(dictionary = "indiana2003", equations = "nc1978")
```

You can change the defaults by specifying a second element in either argument. 

For example:

```{r}
interact(dictionary = "indiana2003", equations = list("nc1978", "male"))
```

`InteRactModel` objects come with built in methods which you can access via the `$` operator. 

```{r}
act$fundamentals("deadbeat")
```

_Note. This is just a simple function that looks inside `act$dictionary`._

## Deflection


```{r}
d <- act$deflection(data.frame(A = "god", B = "kill", O = "deadbeat"))
d
```

You can also extract useful metadata from these scores.

```{r}
get_fundamentals(d)
get_transients(d)
get_element_wise_deflection(d)
```

## Behaviors and Reidentification

Optimal behaviors and/or reidentification uses the deflection scores estimated by `$deflection()` and stored in `d`. They require you specify the perspective of the one doing the behaving or the reidentifying.

Behaviors

```{r}
act$optimal_behavior(d, who = "actor")
act$optimal_behavior(d, who = "object")
```

Reidentification

```{r}
act$reidentify(d, who = "actor")
act$reidentify(d, who = "object")
```

__Closest Terms__

```{r}
act$closest_terms(list(e = 1, p = 0, a = -1), component = "behavior", max_dist = 0.5)

deadbeat <- act$fundamentals("deadbeat")
deadbeat

act$closest_terms(deadbeat, component = "modifier", max_dist = 0.5)
```

## Deference Score

You can also create the deference scores discussed by Freeland & Hoey (2018). 

But this requires to modify the existing dictionary so we get the right combination of identities and behaviors.

This seems to be the easiest way to do this:

```{r}
act <- interact()

defer_to <- act$dictionary |> ## save for later use
  dplyr::filter(term == "defer_to")

occ <- interact(dictionary = "occs2019")
occ$dictionary

occupations <- occ$dictionary$term ## save for later use

## replace original dictionary
occ$dictionary <- dplyr::bind_rows(defer_to, occ$dictionary)
```

Note that a message appeared signaling that the replacement was successful.

```{r}
occ 
```

Now you just create another grid of events, calculate the deflection scores, and average over the As.

```{r}
events <- tidyr::crossing(
  A = occupations,
  B = "defer_to",
  O = occupations
)

output <- occ$deflection(events)

output |> 
  filter(A != O) |> 
  group_by(A) |> 
  summarize(avg = mean(deflection)) |> 
  arrange(desc(avg)) 
```


## Experimental

The things here are still experimental. The API may change a lot.

### Modify Identity

You can create modified identities by combining them with modifier terms in the ACT dictionaries. These use the `traitid` equations in the `actdata` package.

The `$modify_identity` method does not work unless you first specify the `traitid` equation. 

```{r, error=TRUE}
act$modify_identity(list(M = "angry", I = "doctor"))
```

In order to do this you must use the `$add_equation()` method.

```{r}
act$add_equation(type = "traitid", group = "all")
act$modify_identity(list(M = "angry", I = "doctor")) 

act$fundamentals("academic")

grid <- data.frame(
  M = c("tired", "taciturn", "angry", "happy"), 
  I = c("academic", "academic", "academic", "academic")
)

out <- act$modify_identity(grid) 
out |> tidyr::unnest_wider(ratings)
```

### Characteristic Emotion

```{r}
act$add_equation("emotionid", "male")
act$characteristic_emotion(list(I = "brute"))

grid <- act$dictionary |> 
  dplyr::filter(component == "identity") |> 
  dplyr::sample_n(size = 10) |> 
  dplyr::select(I = term)

glimpse(grid)

act$characteristic_emotion(grid)
```


