---
title: "Working With Various Dictionaries"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message=FALSE}
library(tidyverse)
library(actsims)
```

Sometimes we will need to modify existing dictionaries so we get the right combination of identities and behaviors.

*Note. Better documentation coming shortly.*

## Merging Two Different Dictionaries

The following code merges two dictionaries: `usfullsurveyor2015` and `mostafaviestimates2022`.

It uses the `anti_join()` function from the dplyr package to keep all the rows from the `mostafaviestimates2022` dictionary that don't have a match in the `usfullsurveyor2015` dictionary.

```{r}
act <- interact(dictionary = "usfullsurveyor2015")
mostafavi <- interact("mostafaviestimates2022")

new_rows <- dplyr::anti_join(mostafavi$dictionary, act$dictionary)
glimpse(new_rows)

act$dictionary <- dplyr::bind_rows(act$dictionary, new_rows)
act
```

*Note that a message appeared signaling that the replacement was successful.*

You should now be able to use the new extended dictionary.

## Adding Modified Identities

Sometimes we will want to add modified identities, which we can get with the `$modify_identity()` method.

To do this we will first have to add a modifier equation with the `$add_equation()` method and then create a grid of modifiers and identities.

```{r}
act <- interact(dictionary = "usfullsurveyor2015")
act$add_equation(type = "traitid", group = "all")

modifiers <- act$dictionary |> 
  dplyr::filter(component == "modifier") |> 
  ## get thirty random modifiers
  dplyr::slice_sample(n = 30) |> 
  dplyr::pull(term)

identities <- act$dictionary |> 
  dplyr::filter(component == "identity") |> 
  ## get thirty random identities
  dplyr::slice_sample(n = 30) |> 
  dplyr::pull(term)

new_identities <- tidyr::crossing(
  M = modifiers,
  I = identities
)

glimpse(new_identities)

new_rows <- act$modify_identity(new_identities)

glimpse(new_rows)
```

Now we just do as we did before.

```{r}
act$dictionary <- dplyr::bind_rows(act$dictionary, new_rows)
tail(act$dictionary) ## verify that new identities are present.
```
