---
title: "Situations"
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(actsims)
```

## Introduction

These functions power the "Analyze Events" pane in [`interactShiny`](https://acastroaraujo.shinyapps.io/interactShiny/). 

The idea is that each agent in a two-person interaction is an independent `InteRactModel`.

```{r}
situation <- define_situation(
  agent1 = interact(), ## the idea is that each agent can be set up with
  agent2 = interact()  ## different dictionaries and equations.
)
```

The newly created `situation` object contains various fields and functions. 

Most of these will be empty until the `$start()` function is used. 

For example:

```{r}
situation$active  ## one of the two agents will be active at any given time
situation$time
situation$history
```

And here is how they look after `$start()`:

```{r}
situation$start(list(A = "boyfriend", B = "hurt", O = "firefighter"))
opt_beh <- situation$optimal_behavior(who = "agent2")
opt_beh
situation$agent2$closest_terms(opt_beh, component = "behavior")[1:5]

situation$activate("agent2")
situation$new(list(A = "firefighter", B = "babble_to", O = "boyfriend"))

situation$history
```

This `situation` allows for "method chaining" using the `$` operator. This type of code is not very R-like.

```{r}
situation$
  activate("agent1")$
  start(list(A = "employer", B = "hurt", O = "employee"))$ 
  activate("agent2")$
  new(list(A = "employee", B = "pull_away_from", O = "employer"))$
  activate("agent1")$
  new(list(A = "employer", B = "confront", O = "employee"))$
  history
  
situation$history$deflection
```

Instead, you can use R’s pipe operator in tandem with the `sttn_*` functions.

```{r}
df <- situation |> 
  sttn_activate("agent1") |> 
  sttn_start(list(A = "employer", B = "hurt", O = "employee")) |> 
  sttn_activate("agent2") |> 
  sttn_new(list(A = "employee", B = "pull_away_from", O = "employer")) |> 
  sttn_activate("agent1") |> 
  sttn_new(list(A = "employer", B = "confront", O = "employee")) |> 
  sttn_extract()
  
df$deflection
df$transients
```




